Climate control for performant HPUs

### 2014-04-10 docs/draft/draft1.tex
update to manuscript

@@

\subsection*{Priming affects HPU output.}
Before looking for differences in the content of labels provided by workers
from different treatments, we first demonstrate that each treatment has a
distinguishable impact on worker output relative to the \textsc{ambg}.

Using a naive bayes classifier, we are able to distinguish with high precision
and specificity between workers from the \textsc{ambg} treatment and any of
the other 5 treatments.  Fig~\ref{fig:classifier} shows F1-score for a
naive bayes classifier when distinguishing between the \textsc{ambg} and 
target treatments. The classifier was trained using random subsamples of 
output 80 HPUs drawn from each of the \textsc{ambg} and target treatments, and
tested on the ouput of 20 HPUs from each treatment.

We find it remarkable that, using only the labels that workers provide, it is
possible to infer with good accuracy the treatment to which the worker was 
subjected.

\begin{figure*}
	\includegraphics[scale=0.65]{../figs/f1scores.pdf}
	\caption{caption here}
	\label{fig:classifier}
\end{figure*}

A natural question is to test the ability for the classifier to perform 
distinguish between other pairings of treatments.  For example, can the 
classifier distinguish $\textsc{cult}_{img}$ workers from 
$\textsc{cult}_{fund}$ workers?

% Graphics commented out because they make compiling take long!  
% Uncomment when desired!
\begin{figure*}
%	\includegraphics[scale=1.00]{../figs/testImages.png}
	\caption{caption here}
	\label{fig:testImages}
\end{figure*}

@@

\section*{Results}
\begin{figure*}
	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
\end{figure*}

>>>>

\section*{Framework}
At this point we have surveyed some of the conceptual framework traditionally
used to discuss priming in the context of psychology.  Having the origin that
they do, these frameworks are suited to describing the internal mechanisms of
the mind from which they arise.  For our purposes here, we are interested 
primarily in the \textit{effects} of priming, and so it makes sense to 
adopt a position conducive to those ends.  Since our interest in priming 
arises from a desire to construct computing systems from HPUs, we shall
propose a well-defined algorithmic definition for priming.

We must first remark that it does not make sense to speak of an un-primed 
state.  A person can be no more un-primed than a ship at sea can have no 
bearing.  Next, we propose that priming should generally be regarded as a
property of a population of HPUs, rather than as the state of a single HPU.
This is rather like the notion of temperature in thermodynamics.  Although
it does make sense to speak of the kinetic energy of a single molecule, 
Temperature is a statement about the distribution of kinetic energies in a
population of molecules.  The definition of priming which we presently submit
will also be defined in terms of populations.

Two populations, \textsc{j} and \textsc{k} are said to be 
\textit{differently primed} with respect to a task $\mathcal{T}$ if there 
exists a polynomial-time algorithm $\mathcal{A}$ that can distinguish 
(classify) members of \textsc{j} and \textsc{k} with accuracy $\theta$, when 
$\mathcal{A}$ is provided the labelled work-products of HPUs from \textsc{j} 
and \textsc{k} tasked with $\mathcal{T}$.
When $\mathcal{A}$ exists, we say that \textsc{j} and \textsc{k} deviate by 
$\theta$ in priming.

The above definition is simply intended to provide a well-defined definition
of what priming \textit{is}.  Naturally, it says nothing about the consequences
of priming.  The significance of the priming of a given population will
depend both on the nature of $\mathcal{T}$ and on the intended purpose of 
the work products derived from HPUs performing $\mathcal{T}$.

@@

\begin{figure*}
	\begin{center}
		\includegraphics[scale=0.55]{../figs/f1scores.pdf}
		\caption{caption here}
		\label{fig:classifier}
	\end{center}
\end{figure*}

\textbf{Priming affects HPU output.}
Before looking for differences in the content of labels provided by workers
from different treatments, we first demonstrate that the treatments are
distringuishable in an algorithmic sense.

Using a naive bayes classifier, we are able to distinguish with high precision
and specificity between workers from the \textsc{ambg} treatment and any of
the other 5 treatments.  Fig~\ref{fig:classifier}A shows F1-score for a
naive bayes classifier when distinguishing between the \textsc{ambg} and 
the other treatments. The classifier achieves high precision and specificity
in task.  Figure~\ref{fig:classifier}B shows the F1-score for binary
classification between the $\textsc{cult}_{img}$ and the other treatments, 
while \ref{fig:classifier}C shows that for $\textsc{ingr}_{img}$ and the other
treatments.

Not surprisingly, pairs of treatments in which one primes for culture, and the
other primes for ingredients are easily distinguished.  However, it is quite
surprising that high accuracy is achieved when classifying treatments within 
the same valence (e.g. cultural).  This is especially true in such cases as
the classification of  $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$
($\text{F}_1 = 0.863$), where both treatments also share the priming images in 
common.

We find it remarkable that, using only the labels that workers provide, it is
possible to infer with good accuracy (at least when given a choice between 
two posibilities)  the treatment to which the worker was 
subjected.

\begin{figure}
	\includegraphics[scale=0.65]{../figs/valenceComparison.pdf}
	\caption{caption here}
	\label{fig:valence}
\end{figure}

\textbf{Priming orients HPU focus.}
Having established that each treatment does in fact consist of distinguishable 
populations of the HPUs, we next look at the content of labels.  Two of the
root labels in our ontology, \texttt{food} and \texttt{cultural}, map naturally
onto the two concepts that laid behind the design of our priming treatments.
A natural and straightforward expectation is that HPUs from treatments 
$\textsc{cult}_x$ should emit more labels that are ontological descendents of
\texttt{cultural}, while those from the $\textsc{ingr}_x$ treatments should
emit more labels under $\textsc{food}$.

In Fig.~\ref{fig:valence}, we exhibit the percentage of labels having a 
cultural valence (i.e. descending from \texttt{cultural} in the ontology), and 
the percentage having a food valence. Before making comparisons using this
information, we remark that there is no reason to expect a balance in the 
number of words having cultural or food valence overall.  The $\textsc{ambg}$
treatment, which was designed to promote neither valence, exhibits a
significant fraction of words from both the food and cultural valence, while
significantly favoring the former.

Both $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$ show a significant
excess of culturally-oriented labels and fewer food-orientel labels.  
Furthermore, HPUs in these treatments emit more culturally-oriented labels 
even while emitting fewer labes that are simultaneously oriented toward 
cultural and food (light bars in Fig.~\ref{fig:valence}).
The deviation of these treatments from
the others is well beyond the 95\% confidence interval.

Interestingly, the $\textsc{cult}_{fund}$ treatment did not have this effect.
Although we have demonstrated that $\textsc{cult}_{fund}$ is differently
primed from \textsc{ambg} using a naive bayes classifier, in respect of 
overal fraction of food- and culturally-oriented labels, no distinction 
is to be made.

In the case of $\textsc{ingr}_x$ treatments one expects to see an 
enrichment of food-oriented labels. There is perhaps some evidence for this
$\textsc{ingr}_{fund}$ and $\textsc{ingr}_{fund,img}$, but we cannat make any
assertion with confidence.

\begin{figure*}
	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
	\caption{caption here}
	\label{fig:specificity}
\end{figure*}

\textbf{Priming affects attention to detail.}
We next look at how alternately treated HPUs differ in their tendency to use
more specific or more general labels. We use the ontology of labels emitted
on the first test image to unambiguously establish a partial ordering of 
label-specificity.  If one label $\ell_1$ is within the ancestry of another
$\ell_2$, we say that $\ell_1$ is more general than $\ell_2$, otherwise they
are not comparable.  Thus, the label \texttt{naan} is more 
specific than both \texttt{bread} and \texttt{indian}, while uncomparable to
\texttt{statue}.

Label-specificity only generates a partial ordering---at least in our 
experimental design.  A consequence of this is that it is not possible to
assign an overall specificity score to a set of labels.  We submit that this
reflects the underlying complexity of natural language semantics.  While
we admit that there may be many ways to generate full orderings based on some
notion of label specificity, we believe that this would inappropriately 
collapse qualitative differences between labels, leading to results that are
difficult to interpret.

In Fig.~\ref{fig:specificity}, We show pairwise specificity comparisons 
between various pairs of treatments.  Figure~\ref{fig:specificity}A shows
the comparison of \textsc{ambg} with all other treatments.  Both treatments
primed with cultural images ($\textsc{cult}_{img}$ and 
$\textsc{cult}_{fund, img}$) exhibit an excess of more general words compared
to \textsc{ambg}.  Meanwhile, $\textsc{ingr}_{fund}$ emitted an excess of 
more specific words.

We can seek to explain these observations by restricting the comparison to
labels of a specific orientation (e.g. food or cultural).  When we perform
the same comparisons but restricting to food-oriented labels, as shown in 
Fig.~\ref{fig:specificity}G, we see some of the same tendencies as in A.
However, when restricting to culturally-oriented labels 
(Fig~\ref{fig:specificity}D) there are no significant comparative deviations 
in specificity to speak of.

A first conclusion that we can draw from this is that there is a significant
loss of specificity in labels emitted by treatments having non-ambiguous 
priming images.  In Fig.~\ref{fig:specificity}G, only $\textsc{cult}_{fund}$
and $\textsc{ingr}_{fund}$ show no significant deviation.

- through negative priming workers stop responding to generic features of images of prepared meals, which happens in the ambiguous case.

- On the other hand, workers presented with either the cultural or ingredients images are initially struck by the gross differences, which draws generic 
labels, especially with respect to food for which generic labels in ambiguous treatment had been suppressed through negative priming.

- it seems, at first, inconsistent that $\textsc{cult}_{img}$ and 
$\textsc{cult}_{fund,img}$ would at once enrich the fraction of 
culturally-oriented words, but produce no change in the specificity of 
culturally oriented words.  First of all, there is no logical incompatibility
with producing a greater number of cultural terms, yet which are generic 
in nature.  If we follow the hypothesis that focus (or orientation) is directed
by positive priming (perhaps through the subconscious or conscious inference
of reqeuster intent), while focusing on nuances comes from the inhibition
of gross features through negative priming, then this combination of observations makes sense.  Having seen many cultural images, HPUs in 
$\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$ are primed to emit 
cultural labels, however, since the diversity of images is high compared to
other treatments on reaching the test images, there no opportunity for 
focussing in to finer detail through the mechanism of negative priming.

\begin{figure}
	\includegraphics[scale=0.4]{../figs/longitude0.pdf}
	\caption{caption here}
	\label{fig:longitude}
\end{figure}

One interesting test of this hypothesis arises in 
% Graphics commented out because they make compiling take long!  
% Uncomment when desired!
\begin{figure*}
%	\includegraphics[scale=1.00]{../figs/testImages.png}
	\caption{caption here}
	\label{fig:testImages}
\end{figure*}

@@
